Stack Safety as a Security Property

### 2020-07-08 main.tex
Intro to capability machines in threat model

\paragraph*{Capability machines}
%
\rb{TODO Here the policy is built into the hardware, although the extended ISA
  could be split into a machine without capabilities and capabilities as the
  policy.}

>>>>

\paragraph*{Capability machines}
%
Other policies are implemented in hardware or built on such hardware mechanisms.
Capability machines like CHERI \rb{Woodruff+14} extend conventional
architectures to support efficient and fine-grained control over memory
accesses, which can be used to implement security policies involving, for
example, compartmentalization or the stack protection policies of
\citet{Skorstengaard+19,Skorstengaard+19b}. Mapping the underlying protection
mechanisms to policy states and step function would be a delicate operation, as
those are tightly coupled to the hardware design. However, separating the
enforcement aspects of a concrete policy (such as StkTokens, where \(\POLS\)
would encompass details like the abstract call stack, the capability sealing
scheme, etc. \rb{is this digging too deep? or on the contrary, say more?}) from
the machine would be relatively straightforward.
